---
title: "Stats in R Assignment"
author: "Alex Lucchesi"
date: "2023/05/30"
output: html_document
---

## Assignment

For today's assignment, you will be given a blank notebook and a link to the [Call of Duty Dataset](https://www.kaggle.com/datasets/beridzeg45/call-of-duty-reviews) You will need to fill out the notebook and create your own code chunks to run code. Remember that we use this code without any quotation marks to create a code chunk: '`{r} '` \### Your Goal:

To receive credit for today's assignment, you will need to:

-   Import the dataset
-   Load the dataset into a tibble
-   Mutate a new column
-   Create a hypothesis regarding your data and communicate that hypothesis in a scientific method.
-   Create a notebook that has markdown cells, explaining your code and process/thoughts. **Your markdown should be well thought out and reflect a thorough analysis.**
-   Clean the data
-   Explore the data (include visualizations)
-   Create a statistical test and communicate the results

```{r}
library(tidyverse)
```

```{r}
df <- read.csv("C:/Users/aniru/OneDrive/Documents/codingtemple/week7/day3/Call of Duty Reviews.csv")
df
```

```{r}
my_fun <- function(x){
 
  names(x) <- names(x) %>% str_replace_all("\\.", "_")%>%tolower()
    return(x)
}

df <- my_fun(df)

df
```

```{r}
df
```

```{r}
df[!apply(df == "", 1, all), ] 
```

```{r}
df_mut <- mutate(df,total_compund_score=critic_compound_score+user_compound_score)
df_mut
```

```{r}
df_mut <- mutate(df,total_compund_score=critic_compound_score+user_compound_score)
df_mut
```

```{r}
ggplot(data=df, mapping = aes(x=platform, y=metascore)) + 
  geom_point(alpha = 1/10)
```

---
Observation:
  the metascore has increased with respect to critic_compound_score

Question:
  why has there been an increase in the metascore with respect to critic_compound_score?
  
Hypothesize:
null hypothesis-there is no relationship between the increase in the metascore with respect to critic_compound_score
alternate hypothesis-there is a relationship between the increase in the metascore with respect to critic_compound_score

Test:
A comparison test would be performed and then reject or fail to reject one of the hypothesis

Conclusion:
Analyse the results and draw conclusions depending on whether the hypothesis is rejected or not
---

```{r}
ggplot(data=df, mapping = aes(x=platform, y=release_year)) + 
  geom_col()
```

```{r}
set.seed(42)
 
metascore <- rnorm(50, sd = 4.5)
critic_compound_score <- rnorm(50, sd = 4)
 
t.test(metascore, critic_compound_score, var.equal = TRUE)
```

---
 0.1076894   for the mean of x and -0.1605230  for the mean of y the sample means (x and y), which are the sample estimates. In this instance, metascore  mean is 0.1076894 , whereas critic_compound_score mean is -0.1605230 
---
