---
title: "Stats in R Assignment"
author: "Alex Lucchesi"
date: "2023/05/30"
output: html_document
---

## Assignment

For today's assignment, you will be given a blank notebook and a link to the [Call of Duty Dataset](https://www.kaggle.com/datasets/beridzeg45/call-of-duty-reviews) You will need to fill out the notebook and create your own code chunks to run code. Remember that we use this code without any quotation marks to create a code chunk: '`{r} '` \### Your Goal:

To receive credit for today's assignment, you will need to:

-   Import the dataset
-   Load the dataset into a tibble
-   Mutate a new column
-   Create a hypothesis regarding your data and communicate that hypothesis in a scientific method.
-   Create a notebook that has markdown cells, explaining your code and process/thoughts. **Your markdown should be well thought out and reflect a thorough analysis.**
-   Clean the data
-   Explore the data (include visualizations)
-   Create a statistical test and communicate the results

```{r}
library(tidyverse)
```

```{r}
df <- read.csv("C:/Users/aniru/OneDrive/Documents/codingtemple/week7/day3/Call of Duty Reviews.csv")
df
```

```{r}
my_fun <- function(x){
 
  names(x) <- names(x) %>% str_replace_all("\\.", "_")%>%tolower()
    return(x)
}

df <- my_fun(df)

df
```

```{r}
df
```

```{r}
df[!apply(df == "", 1, all), ] 
```

```{r}
df_mut <- mutate(df,total_compund_score=critic_compound_score+user_compound_score)
df_mut
```

```{r}
df_mut <- mutate(df,total_compund_score=critic_compound_score+user_compound_score)
df_mut
```

```{r}
ggplot(data=df, mapping = aes(x=platform, y=metascore)) + 
  geom_point()
```

---
Observation:
  the metascore has relationship with respect to critic_compound_score

Question:
  is there a relationship between metascore  with respect to critic_compound_score?
  
Hypothesize:
null hypothesis-there is no relationship between the metascore with respect to critic_compound_score
alternate hypothesis-there is a relationship between the metascore with respect to critic_compound_score

Test:
A comparison test would be performed and then reject or fail to reject one of the hypothesis

Conclusion:
Analyse the results and draw conclusions depending on whether the hypothesis is rejected or not
---

```{r}
ggplot(data=df, mapping = aes(x=user_compound_score, y=platform)) + 
  geom_col()
```

```{r}
test <- cor.test(df$metascore , df$critic_compound_score)
test
```

---
the correlation coefficient is 0.3352843 which shows weak correlation and since the p-value is 0.002076 which is lesser than 0.05,the results are statistically significant and therefore the null hypothesis would be rejected . 
---
